%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
	\textbf{\Huge \scshape Giulio Starace} \\ \vspace{1pt}
	\today~$|$
	\href{mailto:giulio.starace@gmail.com}{giulio.starace@gmail.com} $|$
	\href{https://github.com/thesofakillers}{github.com/thesofakillers} $|$
	\href{https://www.giuliostarace.com}{giuliostarace.com}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://openai.com}{OpenAI}}{Remote, Anywhere}
{Safety Evaluations Engineer}{Oct 2023 - Dec 2023}
\resumeItemListStart
\resumeItem{
	Short-term contractor role, working on designing, implementing and presenting an eval suite for
	assessing dangerous capabilities of AI models.
}
\resumeItemListEnd

\resumeSubheading
{\href{https://icai.ai/airlab/}{University of Amsterdam - AIRLab}}{Amsterdam, The Netherlands}
{Part-time Researcher (Research Assistant)}{Apr 2022 - Oct 2022}
\resumeItemListStart
\resumeItem{
	Cross-lingual adaptation of large language models (LLMs). Paper and Code:
	\href{https://github.com/thesofakillers/claficle}{github.com/thesofakillers/claficle}
}
\resumeItem{
	Proposed novel ``Post-Hoc Disentanglement via Vessel Adapters (PHoDiVA)'' method.
}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.eso.org}{ESO} - European Southern Observatory}{Cerro Paranal, Chile}
{Research Engineer}{Sep 2020 -- Sep 2021}
\resumeItemListStart
\resumeItem{High-resolution forecasting of Astronomical Seeing using Machine Learning
	methods, using ARIMA and LSTM}
\resumeItem{Led the development of a unified data processing and evaluation
	pipeline: \href{https://pypi.org/project/nowcastlib/}{pypi.org/project/nowcastlib}}
\resumeItemListEnd
\resumeSubSubheading
{Software Engineering Intern}{Aug 2019 -- Jan 2020}
\resumeItemListStart
\resumeItem{Designed, developed, tested and deployed a system for displaying information from the
	observatory's several ticket systems in unified and personalized way via Microsoft Graph API.}
\resumeItemListEnd

\resumeSubheading
{\href{https://video.io/}{Video.io - startup}}{Remote, Anywhere}
{Machine Learning Engineer}{Feb 2020 -- June 2020}
\resumeItemListStart
\resumeItem{Worked on implementing abstractive summarization of dialogic video. (Pandas, Google
	Cloud Speech API).}
\resumeItem{Real time speech to text captioning of live video streams (NodeJS Streams, FFmpeg,
	HLS/DASH video).}
\resumeItem{ Revamped full-stack of internal experimental website (NodeJS, GraphQL, PostgreSQL,
	Docker, NGINX, React). }
\resumeItemListEnd

\resumeSubheading
{\href{https://global.jaxa.jp/}{JAXA} -  Japan Aerospace Exploration Agency}{Sagamihara, Japan}
{Southwestern University}{Aug 2018 -- Oct 2018}
\resumeItemListStart
\resumeItem{ Developed software to estimate visibility of satellite given orbit simulation and
	thermal constraints. }
\resumeItem{ Performed multi-parameter regression on ro-vibrational dataset so to characterize
	starburst galaxy NGC253. }
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{MSc Artificial Intelligence}{GPA: 8.2 (Cum Laude) $|$ Amsterdam, The Netherlands}
{\href{https://www.uva.nl/en}{University of Amsterdam}}{Sep. 2021 -- October 2023}
\resumeItemListStart
\resumeItem{Thesis: Addressing Goal Misgeneralization with Natural Language Interfaces.
	link: \href{https://www.github.com/thesofakillers/nlgoals}{github.com/thesofakillers/nlgoals} }
\resumeItem{Topics of note: Machine Learning, Deep Learning, Natural Language Processing,
	Information Retrieval, \\ Reinforcement Learning, Spiking Neural Networks}
\resumeItemListEnd
\resumeSubheading
{ABC Summer School - Computations in Consciousness and Perception}{Amsterdam, The Netherlands}
{University of Amsterdam}{June 2022}
\resumeItemListStart
\resumeItem{2-week full-time computational neuroscience programme. Developed Project proposal
	available at \href{https://www.giuliostarace.com/ltm/}{giuliostarace.com/ltm}.}
\resumeItemListEnd
\resumeSubheading
{BSc Hons. in Natural Sciences (Physics \& Computer Science)}{ GPA: First Class Honours $|$ Durham, UK}
{\href{https://www.dur.ac.uk/}{\textit{Durham University}}}{Oct. 2016 -- July 2019}
\resumeItemListStart
\resumeItem{ Topics of note: Statistics, Vector Calculus, Linear Algebra, Thermodynamics, Quantum
	\& Particle Physics, Databases, Algorithms and Data-structures, Cryptography and Information,
	Compiler Design, Operating Systems, Computer Vision }
\resumeItemListEnd
\resumeSubHeadingListEnd




%-----------PROJECTS-----------
\section{Projects \& Publications}
\begin{itemize}
	\setlength\itemsep{0em}
	\item Starace et al., \textit{Probing LLMs for Joint Encoding of Linguistic Categories}. Findings
	      of EMNLP 2023. \href{https://arxiv.org/abs/2310.18696}{arXiv:2310.18696}.
	\item van der Togt et al., \textit{[Re] Badder Seeds: Reproducing the Evaluation of Lexical
		      Methods for Bias Measurement}, 2022. ReScience C 8,
	      \#40. \href{https://doi.org/10.5281/zenodo.6574704}{10.5281/zenodo.6574704}.
	\item
	      {\bf \href{https://www.giuliostarace.com/projects/gptrue-or-false/}{GPTrueOrFalse}}
	      Browser extension showing likelihood that given body of text was generated by
	      \href{https://openai.com/blog/better-language-models/}{OpenAI's GPT-2}.
	\item
	      {\bf \href{https://github.com/thesofakillers/iclingo}{iclingo}}
	      Jupyter Kernel for \href{https://en.wikipedia.org/wiki/Answer_set_programming}{answer set
		      programming}  with \href{https://potassco.org/clingo/}{clingo}.
	\item
	      {\bf \href{https://github.com/thesofakillers/bLANS}{bLANS}} Tool for converting sane-LaTeX
	      to \href{https://ans.app/}{ANS}-flavoured LaTeX and viceversa.
\end{itemize}

\section{Miscellaneous Qualities and Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
	Languages             & English (Fluent), Italian (Fluent), Spanish (Professional)                    \\
	Programming Languages & Python, Javascript, SQL, C/C++, HTML/CSS                                      \\
	Libraries             & NumPy, PyTorch, Pandas, HuggingFace, matplotlib, OpenCV, statsmodels, sklearn \\
	Frameworks and Specs  & PyTorch Lightning, WandB, NodeJS (Express), GraphQL, React                    \\
	Technologies          & Vim, Git, tmux, VSCode, ssh, \LaTeX, FFMPEG, Docker, SLURM
\end{tabular}


%-------------------------------------------
\end{document}

